---
title: "Analysing RNAseq Data"
author: "Mohammad Marhabaie"
date: "6 September 2017"
output:
  html_document:
    df_print: paged
    toc: TRUE
    code_folding: show
    toc_depth: 3
editor_options:
  chunk_output_type: inline
---

# Summary
## Background
The **overall** goal of this project is to find which RNA is regulated by Nanos (Nos). 
The **immediate** goal of this report is to analyze RNAseq Data and save them as `.Rda` files. 
## Methods
### Input Data
### Output Data 
### Statistics
## Results
## Conclusion


# Install packages
```{r }

### get packages

## 'http' if 'https' unavailable
# update.packages()

# install.packages(c("data.table", "eulerr","gplots","ggplot2", "ggrepel", "reshape2", "seqinr", "splitstackshape", "VennDiagram","gridExtra","tidyverse","openxlsx","colorspace","colorRamps","ggpubr","dplyr","MASS","ggpmisc", "stringr", "stats")) # EBSeq? plotrix
# 
# if (!requireNamespace("BiocManager", quietly = TRUE))
#   install.packages("BiocManager")
# BiocManager::install(c("edgeR","Biostrings","Biobase")) # "GenomicRanges", , "DESeq2"? "RCurl" ,"GenomicFeatures" ,"rtracklayer" ,"DEXSeq" ,"ShortRead" ,"BiocParallel" ,"motifStack" ,"seqLogo" ,"Rsubread" ,"cummeRbund" ,"multtest"?
# 
# #Bioconductor packages
# # library(EBSeq)
# # library(windowscanr)


# # new ones for GSEA
# BiocManager::install(c("enrichplot", "DOSE", "fgsea", "gage"))
# install.packages(c("ggupset"))

# install.packages("ggridges")

```

# Setting up Basics
First we prepare the paths for the data. 

```{r paths, results="hide", echo=FALSE, warning=FALSE}
#rm(list = ls())
#getwd()
source("helper_code.R")
formula <- y ~ x
load("Data/FBgnID_FBtrID_BDGP6_22_96.RData")
load("Data/all3UTRs_Ensembl_mart_6_22_96.RData")
load("Data/all3UTR_pure.RData")
load("Data/allCDS_r6_22.RData")
```


# --------------------------
# Fisher test for Figure 1
```{r }

## HATCHING
# Nos vs Upf1
fisher.test(matrix(c( 275 ,19, 401, 18),nrow = 2,byrow = T),alternative="two.sided") # p-value = 0.2307, sample estimates odds ratio=   0.6501107
# Upf1-Nos vs Upf1
fisher.test(matrix(c( 275 ,19, 0, 245),nrow = 2,byrow = T),alternative="two.sided") # p-value =< 2.2e-16 , sample estimates odds ratio=  inf
# Upf1-NosL7 vs Upf1
fisher.test(matrix(c( 275 ,19, 326, 57),nrow = 2,byrow = T),alternative="two.sided") # p-value = 0.0005381 , sample estimates odds ratio=   2.52763
# Upf1-NosL7 vs Upf1-Nos
fisher.test(matrix(c( 0 , 246, 326, 57),nrow = 2,byrow = T),alternative="two.sided") # p-value < 2.2e-16 , sample estimates odds ratio=  inf


## DAPI CYCLE 2-13
# Nos vs Upf1
fisher.test(matrix(c( 343, 0, 267, 3),nrow = 2,byrow = T),alternative="two.sided") # p-value = 0.08492 , sample estimates odds ratio=  inf
# Upf1-Nos vs Upf1
fisher.test(matrix(c( 343, 0, 106, 178),nrow = 2,byrow = T),alternative="two.sided") # p-value < 2.2e-16 , sample estimates odds ratio=  inf
# Upf1-NosL7 vs Upf1
fisher.test(matrix(c( 343, 0, 238, 14),nrow = 2,byrow = T),alternative="two.sided") # p-value = 4.826e-06 , sample estimates odds ratio=  inf
# Upf1-NosL7 vs Upf1-Nos
fisher.test(matrix(c( 106, 178, 238, 14),nrow = 2,byrow = T),alternative="two.sided") #  p-value < 2.2e-16 , sample estimates odds ratio=  0.03529591

## EMBRYONIC DEV
# Nos vs Upf1
fisher.test(matrix(c( 280, 15, 297, 16),nrow = 2,byrow = T),alternative="two.sided") # p-value =1 , sample estimates odds ratio=  1.005603
# Upf1-Nos vs Upf1
fisher.test(matrix(c( 280, 15, 2, 466),nrow = 2,byrow = T),alternative="two.sided") # p-value = < 2.2e-16 , sample estimates odds ratio=  4236.491 
# Upf1-Nos vs Upf1
fisher.test(matrix(c( 280, 15, 16, 452),nrow = 2,byrow = T),alternative="two.sided") # p-value = < 2.2e-16 , sample estimates odds ratio=  514.8511  

#fisher.test(matrix(c( 280, 15, 2, 466),nrow = 2,byrow = T),alternative="two.sided") # p-value = < 2.2e-16 , sample estimates odds ratio=  4236.491  


# Upf1-NosL7 vs Upf1
fisher.test(matrix(c( 280, 15, 285, 72),nrow = 2,byrow = T),alternative="two.sided") # p-value = 6.439e-09 , sample estimates odds ratio=  4.706164 
# Upf1-NosL7 vs Upf1-Nos
fisher.test(matrix(c( 16, 452, 285, 72),nrow = 2,byrow = T),alternative="two.sided") # p-value = 2.2e-16 , sample estimates odds ratio=  0.009050626 


```

# Session Information
```{r session_info}

sessionInfo()

```

